\LARGE \bf A Hybrid Control Framework for Autonomous Vehicles at Uncontrolled Intersections

### 2019-01-30 conference/iv2019/manuscript.tex
now ready for read through

As autonomous vehicles (AVs) inch closer to reality, a central requirement for acceptance will be earning the trust of humans in everyday driving situations. In particular, the interaction between AVs and pedestrians is of
high importance, as every human is a pedestrian at some point of the day. This paper considers the interaction of a pedestrian and an autonomous vehicle at a mid-block, uncontrolled intersection where there is ambiguity
over when the pedestrian should cross and when and how the vehicle should yield. By modeling pedestrian behavior through the concept of gap acceptance, the authors show that a hybrid controller with just four distinct modes allows an autonomous vehicle to successfully interact with a pedestrian across a continuous spectrum of possible crosswalk entry behaviors. The controller is validated through extensive simulation, and experimental results are provided on a Hyundai Genesis vehicle for a virtual pedestrian.

@@

\subsection{Statement of Contributions}
Significant research has been conducted to understand the likelihood of pedestrian crossing given certain traffic conditions and pedestrian demographics \cite{Schroeder2011} -\cite{Lee2005}, and a small but growing body of literature develops control strategies for pedestrian avoidance \cite{Bandyopadhyay}-\cite{Thornton2018}. However, what is missing is a contribution that explicitly  tests whether a proposed control strategy is robust to the variety of pedestrian behaviors that have been observed from experimental studies on real roads. What is also missing is analysis of how this controller should behave across multiple traffic scenarios - for example, the navigation problem is different for the pedestrian crossing on the opposing side of traffic, and also depends on which particular lane the vehicle is in.

This paper aims to address this gap by developing a hybrid control architecture that accounts for several distinct pedestrian modes of behavior at an unsignalized crosswalk. An unsignalized crosswalk is chosen as it is the trickiest crosswalk for a pedestrian and vehicle to navigate, as there is no explicit declaration of whose turn it is cross. Simulations show that the hybrid controller is able to handle a continuous spectrum of pedestrian \textit{gap acceptance} behavior, tolerating a range of highly conservative to highly aggressive pedestrians. Moreover, this is possible with just four distinct controller modes. Finally, experimental results are shown on a real vehicle to demonstrate the feasibility of the proposed controller in real-time.

@@

\section{Evaluation Methodology and Simulation Results}

@@

The algorithm is validated in simulation via a built-from-scratch crosswalk simulation environment (Fig. \ref{fig:simFramework}) developed in Python. The simulation environment is built on the ROS robotics interface to enable easy porting of the control architecture to the experimental vehicle in Section \ref{sec:expres}. The simulation includes features such as customizable lanes, the pedestrian crossing on the right or the left, and animation capabilities.

@@

\subsection{Simulation Results}

Figure \ref{fig:velPlot1} shows simulation results for the case where the pedestrian enters the crosswalk on the same side of the road as the vehicle. The left column of the figure is for the case where the vehicle is on the right-most lane of a four way road (marked ``Lane A"), while the right column of the figure is for the case where the vehicle is in the second to right lane (Lane B). Every marker in the figure represents one of 750 simulated vehicle crossings.

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/velPlot.eps}
\caption{Simulation results for case where pedestrian enters the crosswalk on the same side of the road as the vehicle. Plots (a) and (b) show the closest distance between the vehicle and pedestrian for each crossing trial, (c) and (d) plots the average vehicle velocity for each simulated crossing, and (e) and (f) plots the peak acceleration / deceleration magnitude for each trial.}
\label{fig:velPlot1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/velPlot2.eps}
\caption{Simulation results for case where pedestrian enters the crosswalk on the opposite side of the road as the vehicle. Plots (a) and (b) show the closest distance between the vehicle and pedestrian for each crossing trial, (c) and (d) plots the average vehicle velocity for each simulated crossing, and (e) and (f) plots the peak acceleration / deceleration magnitude for each trial.}
\label{fig:velPlot2}
\end{figure}

\subsubsection{Safety and Legality}

@@

\subsubsection{Efficiency}

@@

\begin{table}[h]
\begin{center}
\caption{Average Vehicle Speed}\label{tb:speeds}
\begin{tabular}{cccc}
Pedestrian Entry & Vehicle Lane & Average Speed (m/s) & Pct. of Baseline \\\hline\hline

@@

\subsubsection{Smoothness}
The requirement of keeping a low acceleration magntude where possible is validated through (e) and (f) of Figures~\ref{fig:velPlot1} and \ref{fig:velPlot2}, which plots the peak acceleration / deceleration magnitude for each simulated crossing. The vehicle is able to maintain a peak acceleration of 2 $\mathrm{m/s^2}$ for the vast majority of simulated trials, particularly when the pedestrian crosses from the opposing side of the road or when the vehicle is in the second to right line.

@@

>>>>

As autonomous vehicles (AVs) inch closer to reality, a central requirement for acceptance will be earning the trust of humans in everyday driving situations. In particular, the interaction between AVs and pedestrians is of
high importance, as every human is a pedestrian at some point of the day. This paper considers the interaction of a pedestrian and an autonomous vehicle at a mid-block, uncontrolled intersection where there is ambiguity
over when the pedestrian should cross and when and how the vehicle should yield. By modeling pedestrian behavior through the concept of gap acceptance, the authors show that a hybrid controller with just four distinct modes allows an autonomous vehicle to successfully interact with a pedestrian across a continuous spectrum of possible crosswalk entry behaviors. The controller is validated through extensive simulation and compared to an alternate POMDP solution, and experimental results are provided on a Hyundai Genesis vehicle for a virtual pedestrian.

@@

\subsection{Statement of Contributions}
Significant research has been conducted to understand the likelihood of pedestrian crossing given certain traffic conditions and pedestrian demographics \cite{Schroeder2011} -\cite{Lee2005}, and a small but growing body of literature develops control strategies for pedestrian avoidance \cite{Bandyopadhyay}-\cite{Thornton2018}. However, what is missing is a contribution that explicitly  tests whether a proposed control strategy is robust to the variety of pedestrian behaviors that have been observed from experimental studies on real roads. What is also missing is analysis of how this controller should behave across multiple traffic scenarios - for example, the navigation problem is different for the pedestrian crossing on the opposing side of traffic, and also depends on which particular lane the vehicle is in. To the authors knowledge, there are also no studies that explicitly compare different approaches in order to provide a comparision of alternative solution methods.

This paper aims to address these gap by developing a hybrid control architecture that accounts for several distinct pedestrian modes of behavior at an unsignalized crosswalk. An unsignalized crosswalk is chosen as it is the trickiest crosswalk for a pedestrian and vehicle to navigate, as there is no explicit declaration of whose turn it is cross. Simulations show that the hybrid controller is able to handle a continuous spectrum of pedestrian \textit{gap acceptance} behavior, tolerating a range of highly conservative to highly aggressive pedestrians. Moreover, this is possible with just four distinct controller modes. Additionally, this paper provides a simulated comparison between the hybrid controller and the solution method proposed by Thornton \cite{Thornton2018}, citing advantages and disadvantages of each method. Finally, experimental results are shown on a real vehicle to demonstrate the feasibility of the proposed controller in real-time.

@@

\section{Evaluation Methodology and Comparison with POMDP}

@@

The algorithm is validated in simulation via a built-from-scratch crosswalk simulation environment (Fig. \ref{fig:simFramework}) developed in Python. The simulation environment is built on the ROS robotics interface to enable easy porting of the control architecture to the experimental vehicle in Section \ref{sec:expres}, and for easy comparison to the method provided by Thornton \cite{Thornton2018}. The simulation includes features such as customizable lanes, the pedestrian crossing on the right or the left, and animation capabilities.

@@

\subsection{Alternate Approach - POMDP}
The method proposed by Thornton \cite{Thornton2018} models the unsignalized crosswalk problem as a Partially 
Observable Markov Decision Process (POMDP) \cite{Kochenderfer}. The relevant discretized state variable $x$ is given by

\begin{equation}
x_t = [\dot{d}_t \hspace{2mm} c_t \hspace{2mm} d_t \hspace{2mm} p_t \hspace{2mm} \ddot{d}_{t-1}]^T
\end{equation}

Where $c_t$ is a Boolean variable that is true when the pedestrian is in the crosswalk, $\ddot{d}_{t-1}$ is the previous acceleration command, and $p_t$ is the pedestrian posture, which can be \textit{distracted}, \textit{walking}, or \textit{stopped}. Using a point mass model for the vehicle state transition dynamics and empirical data for the $c_t$dynamics, the authors compute a closed loop policy $\ddot{d}_t = \pi(x_t)$ using the QMDP solver \cite{QMDP}. The reward function that is optimized is given by:

\begin{equation}
r(x_t, \ddot{d}_t) = g_\mathrm{legality} + g_\mathrm{safety} + g_\mathrm{efficient} + g_\mathrm{smooth}
\end{equation}

Where $g_\mathrm{legality}$ and $g_\mathrm{safety}$ are terms encouraging the vehicle to stop when the pedestrian is in the crosswalk, $g_\mathrm{efficient}$ is a term encouraging high velocity when there is no pedestrian, and $g_\mathrm{smooth}$ encourages the vehicle to avoid abrupt changes in acceleration. Note that for our implementation of the method in \cite{Thornton2018}, we assumed $p_t$ was set to \textit{stopped}.

\section{Simulation Results}

Figure \ref{fig:velPlot1} shows simulation results for the case where the pedestrian enters the crosswalk on the same side of the road as the vehicle. The left column of the figure is for the case where the vehicle is on the right-most lane of a four way road (marked ``Lane A"), while the right column of the figure is for the case where the vehicle is in the second to right lane (Lane B). Every marker in the figure represents one of 1500 simulated vehicle crossings, 750 for each method.

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/velPlotBoth.eps}
\caption{Simulation results for case where pedestrian enters the crosswalk on the same side of the road as the vehicle. Plots (a) and (b) show the closest distance between the vehicle and pedestrian for each crossing trial, (c) and (d) plots the average vehicle velocity for each simulated crossing, and (e) and (f) plots the peak acceleration / deceleration magnitude for each trial.}
\label{fig:velPlot1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/velPlot2Both.eps}
\caption{Simulation results for case where pedestrian enters the crosswalk on the opposite side of the road as the vehicle. Plots (a) and (b) show the closest distance between the vehicle and pedestrian for each crossing trial, (c) and (d) plots the average vehicle velocity for each simulated crossing, and (e) and (f) plots the peak acceleration / deceleration magnitude for each trial.}
\label{fig:velPlot2}
\end{figure}

\subsection{Safety and Legality}

@@

\subsubsection{Comparison with POMDP}

In terms of safety and legality, both the POMDP and hybrid controller maintain safe distances from the pedestrian across all trials. For the hybrid controller, this is because the need to stop at $d=0$ is explicitly encoded in the design. For the POMDP, this is due to the reward function terms $g_\mathrm{legality}$ and $g_\mathrm{safety}$

\subsection{Efficiency}

@@

\begin{table}[h]
\begin{center}
\caption{Average Vehicle Speed}\label{tb:speeds}
\begin{tabular}{cccc}
Pedestrian Entry & Vehicle Lane & Hybrid Controller Average Speed (m/s) & POMDP Average Speed \\\hline\hline

@@

\subsubsection{Comparison with POMDP}
The policy from the POMDP displays interesting behavior at low and high pedestrian accepted gaps. At high accepted gaps, even though the pedestrian is waiting for the car to pass before crossing, the POMDP still slows the car down, resulting in a slight drop in average velocity. This is because the POMDP is accounting for the chance that the pedestrian might actually cross at a very low accepted gap. The closed loop POMDP policy does not appear to have knowledge that the vehicle can speed up at the last second. Meanwhile, the hybrid control policy has this case built in, and does not need to slow down if the pedestrian has not entered the crosswalk, resulting in an overall efficiency gain.

Another note is that the POMDP only models the pedestrian as being in the crosswalk or out of the crosswalk - this is necessary to limit the size of the discretized state space for the QMDP solver. This results in the POMDP having the same control policy across all four simulated cases. Because the proposed hybrid controller is continuous, there is no computational burden on accounting for the position and velocity of the pedestrian in the crosswalk. This allows for the controller to consider factors such as time advantage, and continue through the crosswalk in Fig.~\ref{fig:velPlot2}.

\subsection{Smoothness}
The requirement of keeping a low acceleration magntude where possible is validated through (e) and (f) of Figures~\ref{fig:velPlot1} and \ref{fig:velPlot2}, which plots the peak acceleration / deceleration magnitude for each simulated crossing. The vehicle is able to maintain a peak acceleration of 2 $\mathrm{m/s^2}$ for the vast majority of simulated trials, particularly when the pedestrian crosses from the opposing side of the road or when the vehicle is in the second to right line.

@@

\subsubsection{Comparison with POMDP}
Both the POMDP and the hybrid controller must decelerate at a high magnitude when a pedestrian accepts a gap between 1.75-2.5 seconds. One relative advantage of the POMDP is that it is able to decelerate at rates below $a_\mathrm{cmf}$ - at pedestrian accepted gaps of 5-6 seconds, the vehicle decelerates early and at a very low rate in order to avoid excessive jerk. However, by using the same policy for all four simulated scenarios and by not considering the ability to speed through the intersection, the POMDP also tends to decelerate when driving through the intersection would have sufficed.
